---
title: "Field Site Map"
author: "Katie Jackson (modified from Nick's script)"
date: "11 Aug 2023"
output: html_document
---

I needed a really simple, higher-res map for my poster that shows where the sites are in relation to each other and which were inter/subtidal. I modified the script Nick used to make his maps of the environmental conditions since they were already close to what I wanted -- most of the changes were aesthetic.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sf)
library(tidyverse)
library(maptools)
library(ggspatial)
library(here)
```

### Read in shoreline data
Major shorelines files were downloaded from WA DOT (https://geo.wa.gov/datasets/WSDOT::wsdot-major-shorelines-1/about)
```{r}
#read in the shapefile of WA shorelines
shore = st_read("./MajorShorelines.shp")

```

### Create dataframe with site coordinates and types
```{r}
Site = c("Thorndyke", "Chelsea", "Manchester", "Hood Head") 
decLat = c(47.807765, 47.128306, 47.573497, 47.883779)
decLong = c(-122.739104, -122.960099, -122.545168, -122.613236)
farmType = c("Intertidal", "Intertidal", "Subtidal", "Subtidal")
Sites = data.frame(Site, decLat, decLong, farmType)
```


### Site Map
```{r}
site_map = ggplot() +
  #add shoreline from shapefile, wanted it to be a light grey
  geom_sf(data = shore, fill = "#D9D9D9")+
  #add points for each site
  geom_point(data = Sites,
             aes(x = decLong, 
                 y = decLat,
                 fill = Site, #color to match up with the site colors on my poster
                 shape = farmType), #shape to denote sub/intertidal
             color="black", #add black outline around each point
             size = 5,) + #bump up the size for my poster
  #manually assign the colors based on my established color scheme
  scale_fill_manual(values=c("#B3C863", "#756A8C","#037D64", "#CEB08E"))+
  #manually assign the shapes - outlined filled squares (pch=22) for subtidal and circles (pch=21) for intertidal 
  scale_shape_manual(values=c(21, 22))+
  #get rid of axis labels
  xlab(" ") + 
  ylab(" ") +
  #set bounds to zoom in to puget sound
  coord_sf(xlim = c(-123.4, -122), ylim = c(47, 48.2))+
  #change the theme to minimal
  theme_minimal() +
  #add a scale bar
  annotation_scale(location= "bl", width_hint = .25) +
  #add a north arrow
  annotation_north_arrow(location = "tl", #moved it to top left corner
                         style = north_arrow_fancy_orienteering()) +
  theme(axis.text.x = element_blank(), #get rid of the tick marks on the axes
          axis.text.y = element_blank(),
          #legend will be easier to adjust in powerpoint, so I'll just remove it for now (I'll label each site and make a legend for the shapes)
          legend.position = "none",
          #make the grid lines transparent
          panel.grid.major=element_line(colour="transparent"),
          panel.grid.minor=element_line(colour="transparent")
          ) 

site_map #cool

#save the map to the size I need for my poster
#ggsave("./siteMap.png", plot=site_map, width=4.87, height=7.09, units="in")

```

